Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-10 paper/tex/sections/results.tex
Updates from Overleaf

>>>>

\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
In the first panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems. Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect. This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.

However, more surprisingly, we also see that the NSNS distribution extends to higher distances than the other DCOs. The reason for this is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.3$). The BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems. Therefore, despite their relatively higher masses, the maximum distance at which a source is detectable is generally lower than the eccentric NSNSs and hence the distribution tends to zero at smaller distances. Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$. Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution and thus have a low orbital frequencies. The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances. Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted. This means that NSNSs can be seen out to the largest distances of the three DCO types.

\todo{There will also be a little bit more text to explain the example distribution over galaxies in the latter three panels -- will make once Floor combines the latest fiducial simulation data}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
    \caption{\textbf{First panel:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Final three panels:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity. Stars represent an example of the detectable systems in a 4-year LISA mission. Each panel corresponds to a separate DCO type. \todo{make plots}}
    \label{fig:detectable_distance_dist}
\end{figure}
